New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-05 paper/paper.tex
software section

Explain \texttt{radial\_tour}

>>>>

The \citet{tourr} package provides numerous types of tours. An
additional function has been constructed that will generate a sequence
of projections that will decrease the coordinates for \(V_m\) to
\(\boldsymbol{0}\) and back to the original values. It is applicable for
any projection dimension, \(d\).
